Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-19 ICML2019/main.tex
fix formulas

\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\[
\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 GS})},
\]
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\todo{Is it correct
$\lapmechPr{\dataobs}{\ldots}$? }
\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix III)

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
\todo{What is the value of $\varepsilon$?}
%\begin{align*}
%&\lapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
%} = 0.19673467014,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%\end{aligned}
%  } = 0.11932560927,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
%  \end{aligned}
%} = 0.07237464051.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\lapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.19673467014 & t = 0\\
0.11932560927 & t = 1\\
0.07237464051 & t = 2
\end{cases}.
\end{align*}

@@

Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
\todo{
What is the value of $\varepsilon$?
Do we have the formula
\[
\ilapmechPr{\dataobs}{\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}?
\]
}
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%  \end{aligned}
%} = 0.116272079,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
%    \end{aligned}
%} = 0.04277411.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\ilapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.31606027941 & t = 0\\
0.11627207896 & t = 1\\
0.04277410743 & t = 2
\end{cases}.
\end{align*}

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
%The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
%\[
%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
%\]
By the triangle inequality of Hellinger distance,
the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\todo{
Do we need the experimental on this formula?
It is proved mathematically by case analysis.
For any $r \in \mathcal{R}$, we have
\begin{align*}
&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
& = 
\begin{cases}
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive}\\
\hellinger(\bysinfer(\dataobs') - \hellinger(\bysinfer(\dataobs), r)& \text{negative}
\end{cases}\\
& \leq 
\begin{cases}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
\end{cases}\\
&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{align*}
I think it would be a proposition.
}
%In particular, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$.
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
%\end{split}
%\begin{align*}
%LS(\dataobs)
%& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\left|~
%\begin{aligned}
%&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
%&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
%\end{aligned}
%\right|\\
%  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
%\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
%\end{align*}

%\end{equation*}

This equation is validated by an experimental result shown in Fig. \ref{fig_efficiency}. We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$. It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{efficiency.eps}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\label{fig_efficiency}
\end{figure}

>>>>

\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\[
\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 GS})},
\]
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\todo{Is it correct
$\lapmechPr{\dataobs}{\ldots}$? }
\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix III)

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example) and $\epsilon = 1$, we get the following accuracy equations on Laplace mechanism:
%\begin{align*}
%&\lapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
%} = 0.19673467014,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%\end{aligned}
%  } = 0.11932560927,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
%  \end{aligned}
%} = 0.07237464051.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\lapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.19673467014 & t = 0\\
0.11932560927 & t = 1\\
0.07237464051 & t = 2
\end{cases}.
\end{align*}

@@

Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:

\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%  \end{aligned}
%} = 0.116272079,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
%    \end{aligned}
%} = 0.04277411.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\ilapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.31606027941 & t = 0\\
0.11627207896 & t = 1\\
0.04277410743 & t = 2
\end{cases}.
\end{align*}

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
%The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
%\[
%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
%\]
By the triangle inequality of Hellinger distance,
the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\todo{
Do we need the experimental on this formula?
It is proved mathematically by case analysis.
For any $r \in \mathcal{R}$, we have
\begin{align*}
&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
& = 
\begin{cases}
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive}\\
\hellinger(\bysinfer(\dataobs') - \hellinger(\bysinfer(\dataobs), r)& \text{negative}
\end{cases}\\
& \leq 
\begin{cases}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
\end{cases}\\
&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{align*}
I think it would be a proposition.
}

% This equation is validated by an experimental result shown in Fig. \ref{fig_efficiency}. We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$. It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.

% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.45\textwidth]{efficiency.eps}
% \caption{Experimental Results for Finding the Local Sensitivity Efficiently}
% \label{fig_efficiency}
% \end{figure}
